\chapter{Ethical and legal considerations}
\label{chapter8:ethical_legal_considerations}
There are no legal considerations in this project. All user data be anonymized, and the only data logged by the Chat Agent is the questions that the students ask, and the answers 
they are presented with. The greatest ethical concern in this thesis is the invested amount of hours testing the Chat Agent. The students will have projects, deadlines and exams 
to relate to, so requirement of 10-20 hours of usage each month may be too much. On the other hand, if the Chat Agent is not used at all, there may not be enough test data to prove 
whether or not it had any effect on the students learning curve. If one were to set a timed requirement, it could increase the chance of stress and performance anxiety, ending with 
students declining to participate or withdrawing before the testing is completed. It is important for this thesis both that the Chat Agent is used, but also that the users want to 
use it! Another concern in relation to time is that there is no guarantee that the Chat Agent have any beneficial effects on learning. The results may show that it is faster or 
easier to use search engines, meaning students have lost time they could have invested elsewhere.
\vspace{0.5em}\newline
For the validity of the end results, there is also the question of whether or not the Chat Agent actually had any effect. Students past knowledge can effect the average outcome, 
for better or worse. During the thesis, the testing will be conducted by using A/B testing, meaning only a selected group will have access to the Chat Agent. If a large part of the 
group have a lot of knowledge from before, the end results may be mostly False-Positives. Because even though the data show improvement, they improved because they build on previous 
knowledge, and not by use of the Chat Agent. To catch this, one of the questions for each test user will be to grade their own knowledge level to scale the end results. There is 
also the issue that students who might benefit from the Chat Agent, will not be able to use it. Novice students, with little to none programming knowledge may find it unfair that 
they are not the primary selected group. However, by not selecting by type (e.g. knowledge) one can avoid affecting the data and the end results.
